WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-08-14 ms.tex
Nonbreaking spaces

A more open question is how to account for spin precession. The simulations in \cite{FirstTwoYears} and in this paper featured extremely modest spins of $\chi \leq 0.05$, consistent with the fastest known pulsars in binaries \citep{2003Natur.426..531B,DetectingBNSSystemsWithSpin}. The signals were detected using a template bank that lacked spins entirely. Farr et al. (in preparation) show that using nonspinning \ac{BNS} templates for parameter estimation has negligible impact on sky localization. However, if one or both companions are spinning as fast as a millisecond pulsar, $\chi \sim 0.4$ \cite{FastestSpinningMillisecondPulsar}, or even near breakup, $\chi \sim 0.7$, then the orbital plane may precess; in this case, spins can no longer be neglected for detection \cite{DetectingBNSSystemsWithSpin} and may also be important for parameter estimation. Since spinning \ac{BNS} searches are still an active area of development, \ac{BAYESTAR}'s sky localization accuracy in this regime should be reexamined in the future.

Although the response time of \ac{BAYESTAR} has been driven by the anticipated timescales for kilonova and afterglow emission, a recurring question is whether there is any detectable \ac{EM} signal in the seconds before, during, and after the merger itself. Since the \ac{GW} inspiral signal is in principal detectable for up to hundreds of seconds before merger, one could imagine positioning rapidly slewing instruments to search for any prompt emission. This concept was explored by the authors \citep{Cannon:2011vi}, and will be revisted in further detail in both Sathyaprakash et al. (in preparation) and Chu et al. (in preparation).

>>>>

A more open question is how to account for spin precession. The simulations in \cite{FirstTwoYears} and in this paper featured extremely modest spins of $\chi \leq 0.05$, consistent with the fastest known pulsars in binaries \citep{2003Natur.426..531B,DetectingBNSSystemsWithSpin}. The signals were detected using a template bank that lacked spins entirely. Farr et~al. (in preparation) show that using nonspinning \ac{BNS} templates for parameter estimation has negligible impact on sky localization. However, if one or both companions are spinning as fast as a millisecond pulsar, $\chi \sim 0.4$ \cite{FastestSpinningMillisecondPulsar}, or even near breakup, $\chi \sim 0.7$, then the orbital plane may precess; in this case, spins can no longer be neglected for detection \cite{DetectingBNSSystemsWithSpin} and may also be important for parameter estimation. Since spinning \ac{BNS} searches are still an active area of development, \ac{BAYESTAR}'s sky localization accuracy in this regime should be reexamined in the future.

Although the response time of \ac{BAYESTAR} has been driven by the anticipated timescales for kilonova and afterglow emission, a recurring question is whether there is any detectable \ac{EM} signal in the seconds before, during, and after the merger itself. Since the \ac{GW} inspiral signal is in principal detectable for up to hundreds of seconds before merger, one could imagine positioning rapidly slewing instruments to search for any prompt emission. This concept was explored by the authors \citep{Cannon:2011vi}, and will be revisted in further detail in both Sathyaprakash et~al. (in preparation) and Chu et~al. (in preparation).
